cardinalR: Generating interesting high-dimensional data structures

### 2025-08-22 paper-cardinalR.Rmd
Updated some data structures

```{r, eval=FALSE}
langevitour::langevitour(swissroll)
```

@@

```{r, label = "fig-swissroll-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `swissroll` data."}
#| fig-width: 15
#| fig-height: 5

>>>>

```{r}
swissroll_lang <- langevitour::langevitour(swissroll, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r swissroll, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `swissroll` data in $4\\text{-}D$."}

swissrollfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    swissroll_lang
  ),
  device = "xs"
)

class(swissrollfig) <- c(class(swissrollfig), "htmlwidget")

swissrollfig
```

```{r swissroll-proj, eval=knitr::is_latex_output(), fig.pos="H", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `swissroll` data."}
#| fig-width: 15
#| fig-height: 5

### 2025-08-22 paper-cardinalR.tex
Updated some data structures

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-swissroll-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `swissroll` data.}\label{fig:fig-swissroll-proj}
\end{figure}

>>>>

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/swissroll-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `swissroll` data.}\label{fig:swissroll-proj}
\end{figure}
